---
title: "ST2195"
output: 
  pdf_document:
    keep_tex: yes
date: "2024-03-12"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_libraries, warning=FALSE}
library(MASS)
library(ggplot2)
library(data.table)
library(dplyr)
library(zoo)
library(lubridate)
```

# Q1

## Part (a)

```{r q1ai}
# create necessary functions
f = function(x) {
  return(0.5 * exp(-abs(x)))
}

random_walk_metropolis_a = function(x0, N, s) {
  samples = c(x0)
  for (i in 1:N) {
    x_prev = samples[length(samples)]
    x_curr = rnorm(1, mean = x_prev, sd = s)
    ratio = f(x_curr) / f(x_prev)
    u = runif(1)
    if (log(u) < log(ratio)) {
      samples = c(samples, x_curr)
    } else {
      samples = c(samples, x_prev)
    }
  }
  return(samples)
}
```

```{r q1aii, warning=FALSE}
# execute random walk
set.seed(0)

x0 = 0
N = 10000
s = 1

samples = random_walk_metropolis_a(x0, N, s)
true_dist = seq(min(samples), max(samples), length.out = 1000)


combined_plot = ggplot(data.frame(x = samples), aes(x)) +
  geom_histogram(bins = 50, aes(y = ..density.., fill = "Histogram")) +
  geom_density(aes(color = "Kernel Density"), size = 1) +
  geom_line(data = data.frame(x = true_dist, y = f(true_dist)),
            aes(x = x, y = y, color = "True Distribution"),
            size = 1) +
  labs(title = "Random Walk Metropolis Algorithm", x = "x", 
       y = "Probability Density") +
  scale_fill_manual(name = "Legend", values = "lightblue") +
  scale_color_manual(name = "Legend",
                     values = c("Kernel Density" = "red",
                                "True Distribution" = "dark green"))

print(combined_plot)
```

```{r qa1iii, warning=FALSE}
sample_mean = mean(samples)
sample_std = sd(samples)
cat("Sample Mean:", sample_mean, "\n")
cat("Sample Standard Deviation:", sample_std, "\n")
```

## Part (b)

```{r q1bi}
# create necessary functions
random_walk_metropolis_b = function(N, s, J) {
  chains = matrix(nrow = J, ncol = N + 1)
  Mj = c()
  Vj = c()
  x0_lst = rnorm(J, 0, 1)
  
  for (i in 1:J) {
    x0 = x0_lst[i]
    samples = random_walk_metropolis_a(x0, N, s)
    chains[i, ] = samples
    Mj = c(Mj, mean(samples))
    Vj = c(Vj, var(samples))
  }
  
  W = mean(Vj)
  M = mean(Mj)
  B = var(Mj)
  R = sqrt((B + W) / W)
  
  return(R)
}
```

```{r q1bii}
# execute random walk
set.seed(0)
N = 2000
s = 0.001
J = 4
R = random_walk_metropolis_b(N, s, J)
cat("Value of R when N = 2000, s = 0.001, and J = 4:", R, "\n")
```
```{r q1biii}
set.seed(0)
s_lst <- seq(0.001, 1, length.out = 1000)
R_lst <- numeric(length(s_lst))

for (i in seq_along(s_lst)) {
  R_lst[i] <- random_walk_metropolis_b(N, s_lst[i], J)
}

hist(R_lst, breaks = 50, probability = TRUE, col = "lightblue", 
     main = "Histogram of Samples", xlab = "R_lst", ylab = "Density")

```
```{r q1biv}
filtered_R = R_lst[R_lst >= 1 & R_lst <= 1.05]
hist(filtered_R,  breaks = 50, probability = TRUE, col = "lightblue", 
     main = "Histogram of Samples", xlab = "R_lst", ylab = "Density",
     xlim = c(1, 1.05))
```

# Q2

## Part (a)

```{r load_dfs}
df1998 <- fread("dataverse_files/1998.csv.bz2")
```

### 1998 Data

Step by step process is done for the first year of data to clarify what the codes does

```{r isDelayed_column}
# Find the hour that the flight was scheduled to depart
df1998$CRSDepHour <- floor(df1998$CRSDepTime / 100)

# A flight is considered to be delayed if any of the delay variables have a 
# value of 1
df1998$isDelayed <- ifelse(df1998$DepDelay > 0 | 
                           df1998$ArrDelay > 0 | 
                           df1998$CarrierDelay > 0 | 
                           df1998$WeatherDelay > 0 | 
                           df1998$NASDelay > 0 | 
                           df1998$SecurityDelay > 0 | 
                           df1998$LateAircraftDelay > 0, 
                           TRUE, FALSE)

head(df1998)
```

```{r total_flights_per_hour}
# Find the total number of flights that occurred for each hour
df1998_grouped_hour <- df1998 %>% 
  group_by(CRSDepHour) %>%
  summarize(count = n()) %>%
  rename(total_count = count)
df1998_grouped_hour
```

```{r delayed_flights}
# find all delayed flights
df1998_delayed <- df1998 %>%
  filter(isDelayed)
head(df1998_delayed)
```

```{r delayed_flights_per_hour}
# find the number of delayed flights for each hour
df1998_delayed_grouped_hour <- df1998_delayed %>% 
  group_by(CRSDepHour) %>%
  summarize(count = n()) %>%
  rename(delayed_count = count)
df1998_delayed_grouped_hour
```

```{r delayed_prob_per_hour}
# find the historical probability of a flight being delayed for each hour
delayed_prob_hour_1998 = left_join(df1998_grouped_hour, df1998_delayed_grouped_hour,
                              by = 'CRSDepHour')
all_hours = data.frame(CRSDepHour = 0:24)
delayed_prob_hour_1998 = left_join(all_hours, delayed_prob_hour_1998,
                              by = 'CRSDepHour')
delayed_prob_hour_1998 = na.fill(delayed_prob_hour_1998, fill = 0)
delayed_prob_hour_1998 <- as.data.frame(delayed_prob_hour_1998)
delayed_prob_hour_1998$delayed_prob <- delayed_prob_hour_1998$delayed_count / delayed_prob_hour_1998$total_count
delayed_prob_hour_1998
```

```{r plot_delayed_prob1}
barplot(delayed_prob_hour_1998$delayed_prob, names.arg = delayed_prob_hour_1998$CRSDepHour,
        xlab = 'Hour of the Day',
        ylab = 'Historical Probability of Delayed Flights',
        main = 'Historical Probability of Delayed Flights by Hour in 1998',
        col = 'deepskyblue3')
```

```{r total_flights_per_day}
# Find the total number of flights that occurred for each hour
df1998_grouped_day <- df1998 %>% 
  group_by(DayOfWeek) %>%
  summarize(count = n()) %>%
  rename(total_count = count)
df1998_grouped_day
```

```{r delayed_flights_per_day}
# find the number of delayed flights for each day
df1998_delayed_grouped_day <- df1998_delayed %>% 
  group_by(DayOfWeek) %>%
  summarize(count = n()) %>%
  rename(delayed_count = count)
df1998_delayed_grouped_day
```

```{r delayed_prob_per_day}
# find the historical probability of a flight being delayed for each day
delayed_prob_day_1998 = left_join(df1998_grouped_day, df1998_delayed_grouped_day,
                              by = 'DayOfWeek')
delayed_prob_day_1998 = na.fill(delayed_prob_day_1998, fill = 0)
delayed_prob_day_1998 <- as.data.frame(delayed_prob_day_1998)
delayed_prob_day_1998$delayed_prob <- delayed_prob_day_1998$delayed_count / delayed_prob_day_1998$total_count
delayed_prob_day_1998
```

```{r plot_delayed_prob}
barplot(delayed_prob_day_1998$delayed_prob, names.arg = delayed_prob_day_1998$DayOfWeek,
        xlab = 'Day of the Week',
        ylab = 'Historical Probability of Delayed Flights',
        main = 'Historical Probability of Delayed Flights by Day in 1998',
        col = 'deepskyblue3')
```

### 1999 Data
```{r delayed_prob_hr_func}
# create function to reduce repeated code
find_delayed_probability_hour <- function(year) {
  if (year == 2001 | year == 2002) {
    df <- fread(paste0("dataverse_files/", year, ".csv.bz2"), encoding = "Latin-1")
  } else {
    df <- fread(paste0("dataverse_files/", year, ".csv.bz2"))
  }
  
  df <- fread(paste0("dataverse_files/", year, ".csv.bz2"))
  
  # Find the hour that the flight was scheduled to depart
  df$CRSDepHour <- floor(df$CRSDepTime / 100)
  
  # A flight is considered to be delayed if any of the delay variables have a value of 1
  df$isDelayed <- ifelse(df$DepDelay > 0 | 
                                  df$ArrDelay > 0 | 
                                  df$CarrierDelay > 0 | 
                                  df$WeatherDelay > 0 | 
                                  df$NASDelay > 0 | 
                                  df$SecurityDelay > 0 | 
                                  df$LateAircraftDelay > 0, 
                                TRUE, FALSE)
  
  # Find the total number of flights that occurred for each hour
  df_grouped_hour <- df %>% 
    group_by(CRSDepHour) %>%
    summarize(count = n()) %>%
    rename(total_count = count)
  
  # find all delayed flights
  df_delayed <- df %>%
    filter(isDelayed)
  
  # find the number of delayed flights for each hour
  df_delayed_grouped_hour <- df_delayed %>% 
    group_by(CRSDepHour) %>%
    summarize(count = n()) %>%
    rename(delayed_count = count)
  
  # find the historical probability of a flight being delayed for each hour
  delayed_prob <- left_join(df_grouped_hour, df_delayed_grouped_hour, by = 'CRSDepHour')
  all_hours <- data.frame(CRSDepHour = 0:24)
  delayed_prob <- left_join(all_hours, delayed_prob, by = 'CRSDepHour')
  delayed_prob <- na.fill(delayed_prob, fill = 0)
  delayed_prob <- as.data.frame(delayed_prob)
  delayed_prob$delayed_prob <- delayed_prob$delayed_count / delayed_prob$total_count
  print(delayed_prob)
  
  # Create bar plot
  barplot(delayed_prob$delayed_prob, 
          names.arg = delayed_prob$CRSDepHour,
          xlab = 'Hour of the Day',
          ylab = 'Historical Probability of Delayed Flights',
          main = paste('Historical Probability of Delayed Flights by Hour in', year),
          col = 'deepskyblue3')
  
  # Find the total number of flights that occurred for each hour
  df_grouped_day <- df %>% 
    group_by(DayOfWeek) %>%
    summarize(count = n()) %>%
    rename(total_count = count)
  
  # find the number of delayed flights for each day
  df_delayed_grouped_day <- df_delayed %>% 
    group_by(DayOfWeek) %>%
    summarize(count = n()) %>%
    rename(delayed_count = count)
  
  # find the historical probability of a flight being delayed for each day
  delayed_prob_day = left_join(df_grouped_day, df_delayed_grouped_day,
                                by = 'DayOfWeek')
  delayed_prob_day = na.fill(delayed_prob_day, fill = 0)
  delayed_prob_day <- as.data.frame(delayed_prob_day)
  delayed_prob_day$delayed_prob <- delayed_prob_day$delayed_count / delayed_prob_day$total_count
  print(delayed_prob_day)
  
  barplot(delayed_prob_day$delayed_prob, names.arg = delayed_prob_day$DayOfWeek,
        xlab = 'Day of the Week',
        ylab = 'Historical Probability of Delayed Flights',
        main = paste('Historical Probability of Delayed Flights by Hour in', year),
        col = 'deepskyblue3')
}
```

```{r 1999_results}
find_delayed_probability_hour(1999)
```

### 2000 Data
```{r 2000_results}
find_delayed_probability_hour(2000)
```

### 2001 Data
```{r 2001_results}
find_delayed_probability_hour(2001)
```

### 2002 Data
```{r 2002_results}
find_delayed_probability_hour(2002)
```

### 2003 Data
```{r 2003_results}
find_delayed_probability_hour(2003)
```

### 2004 Data
```{r 2004_results}
find_delayed_probability_hour(2004)
```

### 2005 Data
```{r 2005_results}
find_delayed_probability_hour(2005)
```

### 2006 Data
```{r 2006_results}
find_delayed_probability_hour(2006)
```

### 2007 Data
```{r 2007_results}
find_delayed_probability_hour(2007)
```

## Part (b)

### 1998 Data

Step by step process is done for the first year of data to clarify what the codes does

```{r load_dfs2}
plane_data <- read.csv("dataverse_files/plane-data.csv")
tail(plane_data)
```

```{r tailnum_to_year}
# Retrieve tail number and issue date
tailnum_year <- subset(plane_data, select = c("tailnum", "issue_date"))
# convert to date
tailnum_year$issue_date = as.Date(tailnum_year$issue_date, format = "%m/%d/%Y")
# Rename cols to prevent merging issues later on
names(tailnum_year) <- c("TailNum", "issue_date")
tailnum_year = na.omit(tailnum_year)
tailnum_year
```
```{r data_transformation}
# Group by tailnum to find total flights for each tailnum
df1998_grouped_tailnum = df1998 %>%
  group_by(TailNum) %>%
  summarize(count = n()) %>%
  rename(total_count = count)
# Group by tailnum to find dekayed flights for each tailnum
df1998_delayed_grouped_tailnum = df1998_delayed %>%
  group_by(TailNum) %>%
  summarize(count = n()) %>%
  rename(delay_count = count)
# Merge both dataframes together
df1998_grouped_tailnum_merged = inner_join(df1998_grouped_tailnum,
                                          df1998_delayed_grouped_tailnum,
                                          by = "TailNum")
# Merge with tailnum year
df1998_grouped_tailnum_merged = inner_join(df1998_grouped_tailnum_merged,
                                           tailnum_year,
                                           by = "TailNum")
# Create delayed_prob and age columns
df1998_grouped_tailnum_merged$delayed_prob = 
  df1998_grouped_tailnum_merged$delay_count / 
  df1998_grouped_tailnum_merged$total_count
df1998_grouped_tailnum_merged$Age = 1998 -
  year(df1998_grouped_tailnum_merged$issue_date)
# Filter out negative ages and tailnums that have lesser than 100 flights
df1998_grouped_tailnum_merged = df1998_grouped_tailnum_merged %>%
  filter(Age >= 0 & total_count >= 100)
df1998_grouped_tailnum_merged
```


```{r linear_reg}
# run linear reg
model = lm(delayed_prob ~ Age, data = df1998_grouped_tailnum_merged)
summary(model)
```

```{r plot_delayed_prob2}
plot(df1998_grouped_tailnum_merged$Age, df1998_grouped_tailnum_merged$delayed_prob,
     xlab = 'Age of Aircraft',
     ylab = 'Fraction of Flights that are Delayed',
     main = 'Scatter Plot of Age of Aircraft vs 
     Fraction of Delayed Flights in 1998',
     col = 'deepskyblue3', pch = 19)
abline(model, col = 'red')
```

### 1999 Data
```{r part_b_func}
# create function to reduce repeated code
find_delayed_probability_year = function(tailnum_year, year) {
  if (year == 2001 | year == 2002) {
    df <- fread(paste0("dataverse_files/", year, ".csv.bz2"), encoding = "Latin-1")
  } else {
    df <- fread(paste0("dataverse_files/", year, ".csv.bz2"))
  }
  
  # A flight is considered to be delayed if any of the delay variables have a 
  # value of 1
  df$isDelayed <- ifelse(df$DepDelay > 0 | 
                                  df$ArrDelay > 0 | 
                                  df$CarrierDelay > 0 | 
                                  df$WeatherDelay > 0 | 
                                  df$NASDelay > 0 | 
                                  df$SecurityDelay > 0 | 
                                  df$LateAircraftDelay > 0, 
                                TRUE, FALSE)
  
  # find all delayed flights
  df_delayed <- df %>%
    filter(isDelayed)
  
  # Group by tailnum to find total flights for each tailnum
  df_grouped_tailnum = df %>%
    group_by(TailNum) %>%
    summarize(count = n()) %>%
    rename(total_count = count)
  # Group by tailnum to find dekayed flights for each tailnum
  df_delayed_grouped_tailnum = df_delayed %>%
    group_by(TailNum) %>%
    summarize(count = n()) %>%
    rename(delay_count = count)
  # Merge both dataframes together
  df_grouped_tailnum_merged = inner_join(df_grouped_tailnum,
                                            df_delayed_grouped_tailnum,
                                            by = "TailNum")
  # Merge with tailnum year
  df_grouped_tailnum_merged = inner_join(df_grouped_tailnum_merged,
                                             tailnum_year,
                                             by = "TailNum")
  # Create delayed_prob and age columns
  df_grouped_tailnum_merged$delayed_prob = 
    df_grouped_tailnum_merged$delay_count / 
    df_grouped_tailnum_merged$total_count
  df_grouped_tailnum_merged$Age = year -
    year(df_grouped_tailnum_merged$issue_date)
  # Filter out negative ages and tailnums that have lesser than 100 flights
  df_grouped_tailnum_merged = df_grouped_tailnum_merged %>%
    filter(Age >= 0 & total_count >= 100)
  
  # run linear reg
  model = lm(delayed_prob ~ Age, data = df_grouped_tailnum_merged)
  print(summary(model))
  
  plot(df_grouped_tailnum_merged$Age, df_grouped_tailnum_merged$delayed_prob,
     xlab = 'Age of Aircraft',
     ylab = 'Fraction of Flights that are Delayed',
     main = paste('Scatter Plot of Age of Aircraft vs 
     Fraction of Delayed Flights in', year),
     col = 'deepskyblue3', pch = 19)
abline(model, col = 'red')
}
```

```{r 1999_results2}
find_delayed_probability_year(tailnum_year, 1999)
```

### 2000 Data
```{r 2000_results2}
find_delayed_probability_year(tailnum_year, 2000)
```

### 2001 Data
```{r 2001_results2}
find_delayed_probability_year(tailnum_year, 2001)
```

### 2002 Data
```{r 2002_results2}
find_delayed_probability_year(tailnum_year, 2002)
```

### 2003 Data
```{r 2003_results2}
find_delayed_probability_year(tailnum_year, 2003)
```

### 2004 Data
```{r 2004_results2}
find_delayed_probability_year(tailnum_year, 2004)
```

### 2005 Data
```{r 2005_results2}
find_delayed_probability_year(tailnum_year, 2005)
```

### 2006 Data
```{r 2006_results2}
find_delayed_probability_year(tailnum_year, 2006)
```

### 2007 Data
```{r 2007_results2}
find_delayed_probability_year(tailnum_year, 2007)
```

## Part (c)

### 1998 Data

Step by step process is done for the first year to clarify what the code does

```{r}
airports <- read.csv("dataverse_files/airports.csv")
airports_coord <- airports[, c("iata", "lat", "long")]
head(airports_coord)
```

```{r}
# get estimated hour of arrival
df1998$CRSArrHour = floor(df1998$CRSArrTime / 100)
# get week of the month
df1998$WeekofMonth = floor(df1998$DayofMonth / 7)
# # Change boolean column to integer column
# df1998$isDelayed[is.na(df1998$isDelayed)] = FALSE
# df1998$isDelayed <- as.integer(df1998$isDelayed)

# Create dataframe with columns for logistic regression
reg_cols <- c('Month', 'WeekofMonth', 'DayOfWeek', 'CRSDepHour', 'CRSArrHour', 
              'UniqueCarrier', 'Origin', 'Dest', 'Distance', 'Diverted')
df1998_reg <- df1998[, ..reg_cols]

# Join to get lat and long for origin airport
airports_coord = airports_coord %>%
  rename(Origin = iata)
df1998_reg <- left_join(df1998_reg, airports_coord, by = "Origin")

# Join to get lat and long for destination airport
airports_coord = airports_coord %>%
  rename(Dest = Origin)
df1998_reg <- left_join(df1998_reg, airports_coord, by = "Dest")

# Drop Origin and Dest to prevent multicollinearity
df1998_reg <- subset(df1998_reg, select = -c(Origin, Dest))
df1998_reg = df1998_reg %>%
  rename(dest_lat = lat.y, dest_long = long.y,
         origin_lat = lat.x, origin_long = long.x)

# Restore airports_coord to original naming
airports_coord = airports_coord %>%
  rename(iata = Dest)

head(df1998_reg)
```

```{r}
# run logistic regression
log_reg = glm(Diverted ~ Month + WeekofMonth + DayOfWeek + CRSDepHour + 
              CRSArrHour + UniqueCarrier + Distance + origin_lat + origin_long +
              dest_lat + dest_long, data = df1998_reg, family = binomial)
summary(log_reg)
```


```{r}
# store coefficients into a df
coef_df <- data.frame(year = 1998:2007)
for (var in names(coef(log_reg))) {
    coef_df[1, var] = coef(log_reg)[var]
}
coef_df
```

### 1999 Data
```{r}
#create function
get_coefficients = function(airports_coord, reg_cols, coef_df, year) {
  if (year == 2001 | year == 2002) {
    df <- fread(paste0("dataverse_files/", year, ".csv.bz2"), encoding = "Latin-1")
  } else {
    df <- fread(paste0("dataverse_files/", year, ".csv.bz2"))
  }
  
  # Find the hour that the flight was scheduled to depart
  df$CRSDepHour <- floor(df$CRSDepTime / 100)
  
  # A flight is considered to be delayed if any of the delay variables have a 
  # value of 1
  df$isDelayed <- ifelse(df$DepDelay > 0 | 
                                  df$ArrDelay > 0 | 
                                  df$CarrierDelay > 0 | 
                                  df$WeatherDelay > 0 | 
                                  df$NASDelay > 0 | 
                                  df$SecurityDelay > 0 | 
                                  df$LateAircraftDelay > 0, 
                                TRUE, FALSE)
  
  # get estimated hour of arrival
  df$CRSArrHour = floor(df$CRSArrTime / 100)
  # get week of the month
  df$WeekofMonth = floor(df$DayofMonth / 7)
  # # Change boolean column to integer column
  # df$isDelayed[is.na(df$isDelayed)] = FALSE
  # df$isDelayed <- as.integer(df$isDelayed)
  
  # Create dataframe with columns for logistic regression
  df_reg <- df[, ..reg_cols]
  
  # Join to get lat and long for origin airport
  airports_coord = airports_coord %>%
    rename(Origin = iata)
  df_reg <- left_join(df_reg, airports_coord, by = "Origin")
  
  # Join to get lat and long for destination airport
  airports_coord = airports_coord %>%
    rename(Dest = Origin)
  df_reg <- left_join(df_reg, airports_coord, by = "Dest")
  
  # Drop Origin and Dest to prevent multicollinearity
  df_reg <- subset(df_reg, select = -c(Origin, Dest))
  df_reg = df_reg %>%
    rename(dest_lat = lat.y, dest_long = long.y,
           origin_lat = lat.x, origin_long = long.x)
  
  # Restore airports_coord to original naming
  airports_coord = airports_coord %>%
    rename(iata = Dest)
  
  # run logistic regression
  log_reg = glm(Diverted ~ Month + WeekofMonth + DayOfWeek + CRSDepHour + 
                CRSArrHour + UniqueCarrier + Distance + origin_lat + origin_long +
                dest_lat + dest_long, data = df_reg, family = binomial)
  print(summary(log_reg))
  
  # store coefficients into a df
  for (var in names(coef(log_reg))) {
    coef_df[year-1997, var] = coef(log_reg)[var]
  }
  return(coef_df)
}
```

```{r 1999_coefs}
reg_cols <- c('Month', 'WeekofMonth', 'DayOfWeek', 'CRSDepHour', 'CRSArrHour', 
              'UniqueCarrier', 'Origin', 'Dest', 'Distance', 'Diverted')
coef_df <- data.frame(year = 1998:2007)
coef_df = get_coefficients(airports_coord, reg_cols, coef_df, 1999)
```

### 2000 Data
```{r 2000_coefs}
coef_df = get_coefficients(airports_coord, reg_cols, coef_df, 2000)
```

### 2001 Data
```{r 2001_coefs}
coef_df = get_coefficients(airports_coord, reg_cols, coef_df, 2001)
```

### 2002 Data
```{r 2002_coefs}
coef_df = get_coefficients(airports_coord, reg_cols, coef_df, 2002)
```

### 2003 Data
```{r 2003_coefs}
coef_df = get_coefficients(airports_coord, reg_cols, coef_df, 2003)
```

### 2004 Data
```{r 2004_coefs}
coef_df = get_coefficients(airports_coord, reg_cols, coef_df, 2004)
```

### 2005 Data
```{r 2005_coefs}
coef_df = get_coefficients(airports_coord, reg_cols, coef_df, 2005)
```

### 2006 Data
```{r 2006_coefs}
coef_df = get_coefficients(airports_coord, reg_cols, coef_df, 2006)
```

### 2007 Data
```{r 2007_coefs}
coef_df = get_coefficients(airports_coord, reg_cols, coef_df, 2007)
```


```{r}
coef_df
```

```{r}
ggplot(coef_df, aes(x = year, y = `(Intercept)`)) +
  geom_line() +
  labs(x = "Year", y = "(Intercept)") + 
  ggtitle("Line Chart of Coefficient of (Intercept) Over Years") +
  scale_x_continuous(breaks = seq(min(coef_df$year), max(coef_df$year), by = 1),
                     labels = seq(min(coef_df$year), max(coef_df$year), by = 1))
```

```{r}
ggplot(coef_df, aes(x = year, y = Month)) +
  geom_line() +
  labs(x = "Year", y = "Month") + 
  ggtitle("Line Chart of Coefficient of Month Over Years") +
  scale_x_continuous(breaks = seq(min(coef_df$year), max(coef_df$year), by = 1),
                     labels = seq(min(coef_df$year), max(coef_df$year), by = 1))
```

```{r}
ggplot(coef_df, aes(x = year, y = WeekofMonth)) +
  geom_line() +
  labs(x = "Year", y = "WeekofMonth") + 
  ggtitle("Line Chart of Coefficient of WeekofMonth Over Years") +
  scale_x_continuous(breaks = seq(min(coef_df$year), max(coef_df$year), by = 1),
                     labels = seq(min(coef_df$year), max(coef_df$year), by = 1))
```

```{r}
ggplot(coef_df, aes(x = year, y = DayOfWeek)) +
  geom_line() +
  labs(x = "Year", y = "DayOfWeek") + 
  ggtitle("Line Chart of Coefficient of DayOfWeek Over Years") +
  scale_x_continuous(breaks = seq(min(coef_df$year), max(coef_df$year), by = 1),
                     labels = seq(min(coef_df$year), max(coef_df$year), by = 1))
```

```{r}
ggplot(coef_df, aes(x = year, y = CRSDepHour)) +
  geom_line() +
  labs(x = "Year", y = "CRSDepHour") + 
  ggtitle("Line Chart of Coefficient of CRSDepHour Over Years") +
  scale_x_continuous(breaks = seq(min(coef_df$year), max(coef_df$year), by = 1),
                     labels = seq(min(coef_df$year), max(coef_df$year), by = 1))
```

```{r}
ggplot(coef_df, aes(x = year, y = CRSArrHour)) +
  geom_line() +
  labs(x = "Year", y = "CRSArrHour") + 
  ggtitle("Line Chart of Coefficient of CRSArrHour Over Years") +
  scale_x_continuous(breaks = seq(min(coef_df$year), max(coef_df$year), by = 1),
                     labels = seq(min(coef_df$year), max(coef_df$year), by = 1))
```

```{r}
ggplot(coef_df, aes(x = year, y = Distance)) +
  geom_line() +
  labs(x = "Year", y = "Distance") + 
  ggtitle("Line Chart of Coefficient of Distance Over Years") +
  scale_x_continuous(breaks = seq(min(coef_df$year), max(coef_df$year), by = 1),
                     labels = seq(min(coef_df$year), max(coef_df$year), by = 1))
```

```{r}
ggplot(coef_df, aes(x = year, y = origin_lat)) +
  geom_line() +
  labs(x = "Year", y = "origin_lat") + 
  ggtitle("Line Chart of Coefficient of origin_lat Over Years") +
  scale_x_continuous(breaks = seq(min(coef_df$year), max(coef_df$year), by = 1),
                     labels = seq(min(coef_df$year), max(coef_df$year), by = 1))
```

```{r}
ggplot(coef_df, aes(x = year, y = origin_long)) +
  geom_line() +
  labs(x = "Year", y = "origin_long") + 
  ggtitle("Line Chart of Coefficient of origin_long Over Years") +
  scale_x_continuous(breaks = seq(min(coef_df$year), max(coef_df$year), by = 1),
                     labels = seq(min(coef_df$year), max(coef_df$year), by = 1))
```

```{r}
ggplot(coef_df, aes(x = year, y = dest_lat)) +
  geom_line() +
  labs(x = "Year", y = "dest_lat") + 
  ggtitle("Line Chart of Coefficient of dest_lat Over Years") +
  scale_x_continuous(breaks = seq(min(coef_df$year), max(coef_df$year), by = 1),
                     labels = seq(min(coef_df$year), max(coef_df$year), by = 1))
```

```{r}
ggplot(coef_df, aes(x = year, y = dest_long)) +
  geom_line() +
  labs(x = "Year", y = "dest_long") + 
  ggtitle("Line Chart of Coefficient of dest_long Over Years") +
  scale_x_continuous(breaks = seq(min(coef_df$year), max(coef_df$year), by = 1),
                     labels = seq(min(coef_df$year), max(coef_df$year), by = 1))
```

```{r}
ggplot(coef_df, aes(x = year, y = UniqueCarrierAS)) +
  geom_line() +
  labs(x = "Year", y = "UniqueCarrierAS") + 
  ggtitle("Line Chart of Coefficient of UniqueCarrierAS Over Years") +
  scale_x_continuous(breaks = seq(min(coef_df$year), max(coef_df$year), by = 1),
                     labels = seq(min(coef_df$year), max(coef_df$year), by = 1))
```

```{r}
ggplot(coef_df, aes(x = year, y = UniqueCarrierCO)) +
  geom_line() +
  labs(x = "Year", y = "UniqueCarrierCO") + 
  ggtitle("Line Chart of Coefficient of UniqueCarrierCO Over Years") +
  scale_x_continuous(breaks = seq(min(coef_df$year), max(coef_df$year), by = 1),
                     labels = seq(min(coef_df$year), max(coef_df$year), by = 1))
```

```{r}
ggplot(coef_df, aes(x = year, y = UniqueCarrierDL)) +
  geom_line() +
  labs(x = "Year", y = "UniqueCarrierDL") + 
  ggtitle("Line Chart of Coefficient of UniqueCarrierDL Over Years") +
  scale_x_continuous(breaks = seq(min(coef_df$year), max(coef_df$year), by = 1),
                     labels = seq(min(coef_df$year), max(coef_df$year), by = 1))
```

```{r}
ggplot(coef_df, aes(x = year, y = UniqueCarrierHP)) +
  geom_line() +
  labs(x = "Year", y = "UniqueCarrierHP") + 
  ggtitle("Line Chart of Coefficient of UniqueCarrierHP Over Years") +
  scale_x_continuous(breaks = seq(min(coef_df$year), max(coef_df$year), by = 1),
                     labels = seq(min(coef_df$year), max(coef_df$year), by = 1))
```

```{r}
ggplot(coef_df, aes(x = year, y = UniqueCarrierNW)) +
  geom_line() +
  labs(x = "Year", y = "UniqueCarrierNW") + 
  ggtitle("Line Chart of Coefficient of UniqueCarrierNW Over Years") +
  scale_x_continuous(breaks = seq(min(coef_df$year), max(coef_df$year), by = 1),
                     labels = seq(min(coef_df$year), max(coef_df$year), by = 1))
```

```{r}
ggplot(coef_df, aes(x = year, y = UniqueCarrierTW)) +
  geom_line() +
  labs(x = "Year", y = "UniqueCarrierTW") + 
  ggtitle("Line Chart of Coefficient of UniqueCarrierTW Over Years") +
  scale_x_continuous(breaks = seq(min(coef_df$year), max(coef_df$year), by = 1),
                     labels = seq(min(coef_df$year), max(coef_df$year), by = 1))
```

```{r}
ggplot(coef_df, aes(x = year, y = UniqueCarrierUA)) +
  geom_line() +
  labs(x = "Year", y = "UniqueCarrierUA") + 
  ggtitle("Line Chart of Coefficient of UniqueCarrierUA Over Years") +
  scale_x_continuous(breaks = seq(min(coef_df$year), max(coef_df$year), by = 1),
                     labels = seq(min(coef_df$year), max(coef_df$year), by = 1))
```

```{r}
ggplot(coef_df, aes(x = year, y = UniqueCarrierUS)) +
  geom_line() +
  labs(x = "Year", y = "UniqueCarrierUS") + 
  ggtitle("Line Chart of Coefficient of UniqueCarrierUS Over Years") +
  scale_x_continuous(breaks = seq(min(coef_df$year), max(coef_df$year), by = 1),
                     labels = seq(min(coef_df$year), max(coef_df$year), by = 1))
```

```{r}
ggplot(coef_df, aes(x = year, y = UniqueCarrierWN)) +
  geom_line() +
  labs(x = "Year", y = "UniqueCarrierWN") + 
  ggtitle("Line Chart of Coefficient of UniqueCarrierWN Over Years") +
  scale_x_continuous(breaks = seq(min(coef_df$year), max(coef_df$year), by = 1),
                     labels = seq(min(coef_df$year), max(coef_df$year), by = 1))
```

```{r}
ggplot(coef_df, aes(x = year, y = UniqueCarrierAQ)) +
  geom_line() +
  labs(x = "Year", y = "UniqueCarrierAQ") + 
  ggtitle("Line Chart of Coefficient of UniqueCarrierAQ Over Years") +
  scale_x_continuous(breaks = seq(min(coef_df$year), max(coef_df$year), by = 1),
                     labels = seq(min(coef_df$year), max(coef_df$year), by = 1))
```

```{r}
ggplot(coef_df, aes(x = year, y = UniqueCarrierMQ)) +
  geom_line() +
  labs(x = "Year", y = "UniqueCarrierMQ") + 
  ggtitle("Line Chart of Coefficient of UniqueCarrierMQ Over Years") +
  scale_x_continuous(breaks = seq(min(coef_df$year), max(coef_df$year), by = 1),
                     labels = seq(min(coef_df$year), max(coef_df$year), by = 1))
```

```{r}
ggplot(coef_df, aes(x = year, y = UniqueCarrierB6)) +
  geom_line() +
  labs(x = "Year", y = "UniqueCarrierB6") + 
  ggtitle("Line Chart of Coefficient of UniqueCarrierB6 Over Years") +
  scale_x_continuous(breaks = seq(min(coef_df$year), max(coef_df$year), by = 1),
                     labels = seq(min(coef_df$year), max(coef_df$year), by = 1))
```

```{r}
ggplot(coef_df, aes(x = year, y = UniqueCarrierDH)) +
  geom_line() +
  labs(x = "Year", y = "UniqueCarrierDH") + 
  ggtitle("Line Chart of Coefficient of UniqueCarrierDH Over Years") +
  scale_x_continuous(breaks = seq(min(coef_df$year), max(coef_df$year), by = 1),
                     labels = seq(min(coef_df$year), max(coef_df$year), by = 1))
```

```{r}
ggplot(coef_df, aes(x = year, y = UniqueCarrierEV)) +
  geom_line() +
  labs(x = "Year", y = "UniqueCarrierEV") + 
  ggtitle("Line Chart of Coefficient of UniqueCarrierEV Over Years") +
  scale_x_continuous(breaks = seq(min(coef_df$year), max(coef_df$year), by = 1),
                     labels = seq(min(coef_df$year), max(coef_df$year), by = 1))
```

```{r}
ggplot(coef_df, aes(x = year, y = UniqueCarrierFL)) +
  geom_line() +
  labs(x = "Year", y = "UniqueCarrierFL") + 
  ggtitle("Line Chart of Coefficient of UniqueCarrierFL Over Years") +
  scale_x_continuous(breaks = seq(min(coef_df$year), max(coef_df$year), by = 1),
                     labels = seq(min(coef_df$year), max(coef_df$year), by = 1))
```

```{r}
ggplot(coef_df, aes(x = year, y = UniqueCarrierHA)) +
  geom_line() +
  labs(x = "Year", y = "UniqueCarrierHA") + 
  ggtitle("Line Chart of Coefficient of UniqueCarrierHA Over Years") +
  scale_x_continuous(breaks = seq(min(coef_df$year), max(coef_df$year), by = 1),
                     labels = seq(min(coef_df$year), max(coef_df$year), by = 1))
```

```{r}
ggplot(coef_df, aes(x = year, y = UniqueCarrierOO)) +
  geom_line() +
  labs(x = "Year", y = "UniqueCarrierOO") + 
  ggtitle("Line Chart of Coefficient of UniqueCarrierOO Over Years") +
  scale_x_continuous(breaks = seq(min(coef_df$year), max(coef_df$year), by = 1),
                     labels = seq(min(coef_df$year), max(coef_df$year), by = 1))
```

```{r}
ggplot(coef_df, aes(x = year, y = UniqueCarrierTZ)) +
  geom_line() +
  labs(x = "Year", y = "UniqueCarrierTZ") + 
  ggtitle("Line Chart of Coefficient of UniqueCarrierTZ Over Years") +
  scale_x_continuous(breaks = seq(min(coef_df$year), max(coef_df$year), by = 1),
                     labels = seq(min(coef_df$year), max(coef_df$year), by = 1))
```

```{r}
ggplot(coef_df, aes(x = year, y = UniqueCarrierXE)) +
  geom_line() +
  labs(x = "Year", y = "UniqueCarrierXE") + 
  ggtitle("Line Chart of Coefficient of UniqueCarrierXE Over Years") +
  scale_x_continuous(breaks = seq(min(coef_df$year), max(coef_df$year), by = 1),
                     labels = seq(min(coef_df$year), max(coef_df$year), by = 1))
```

```{r}
ggplot(coef_df, aes(x = year, y = UniqueCarrierOH)) +
  geom_line() +
  labs(x = "Year", y = "UniqueCarrierOH") + 
  ggtitle("Line Chart of Coefficient of UniqueCarrierOH Over Years") +
  scale_x_continuous(breaks = seq(min(coef_df$year), max(coef_df$year), by = 1),
                     labels = seq(min(coef_df$year), max(coef_df$year), by = 1))
```

```{r}
ggplot(coef_df, aes(x = year, y = UniqueCarrierF9)) +
  geom_line() +
  labs(x = "Year", y = "UniqueCarrierF9") + 
  ggtitle("Line Chart of Coefficient of UniqueCarrierF9 Over Years") +
  scale_x_continuous(breaks = seq(min(coef_df$year), max(coef_df$year), by = 1),
                     labels = seq(min(coef_df$year), max(coef_df$year), by = 1))
```

```{r}
ggplot(coef_df, aes(x = year, y = UniqueCarrierYV)) +
  geom_line() +
  labs(x = "Year", y = "UniqueCarrierYV") + 
  ggtitle("Line Chart of Coefficient of UniqueCarrierYV Over Years") +
  scale_x_continuous(breaks = seq(min(coef_df$year), max(coef_df$year), by = 1),
                     labels = seq(min(coef_df$year), max(coef_df$year), by = 1))
```

```{r}
ggplot(coef_df, aes(x = year, y = UniqueCarrierAA)) +
  geom_line() +
  labs(x = "Year", y = "UniqueCarrierAA") + 
  ggtitle("Line Chart of Coefficient of UniqueCarrierAA Over Years") +
  scale_x_continuous(breaks = seq(min(coef_df$year), max(coef_df$year), by = 1),
                     labels = seq(min(coef_df$year), max(coef_df$year), by = 1))
```



